\input{preamble}
%% end of preamble

\usepackage{framed}
\usepackage[inline]{enumitem}
\usepackage[backend=bibtex]{biblatex}
\usepackage{amssymb}
\usepackage{amsmath}

\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}

\usepackage{multirow}
\usepackage{booktabs}


\title[]{\Huge \textbf{\textcolor{black}{A Machine Learning Refresher}}}
\subtitle{\Large Q \& A on the main concepts and terminology}
% \author{\large \textbf{Huascar A. Sanchez}}
\author[HAS]{
% \author[HAS \& DS]{
\parbox[t]{1.5in}{Huascar Sanchez \\\small\texttt{no.email.now}} %\hspace{.3in}
% \and
% \parbox[t]{1.5in}{Second Author \\\small\texttt{second.author@sri.com}}
}
\institute[]{\large Some Research Lab}

\date{\today}

% Left align title page
\makeatletter
\setbeamertemplate{title page}[default][left,colsep=-4bp,rounded=true,shadow=\beamer@themerounded@shadow]
\makeatother

\begin{document}
%%% TIKZ STUFF
\tikzset{
        every picture/.style={remember picture,baseline},
        every node/.style={anchor=base,align=center,outer sep=1.5pt},
        every path/.style={thick},
        }
\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture]
        \node (marker-#1-a) at (-.3em,.3em) {};%
}
\newcommand\markbottomright[2]{%
    \tikz[overlay,remember picture]
        \node (marker-#1-b) at (0em,0em) {};%
}
\tikzstyle{every picture}+=[remember picture]
\tikzstyle{mybox} =[draw=black, very thick, rectangle, inner sep=10pt, inner ysep=20pt]
\tikzstyle{mybox2} =[draw=black, very thick, rectangle, inner sep=5pt, inner ysep=10pt]
\tikzstyle{fancytitle} =[draw=black,fill=red, text=white]
%%%% END TIKZ STUFF

% Title Slide
\begin{frame}
\maketitle
% \centering
\tiny\hspace{1em}The views expressed do not necessarily reflect the position of my employer.
\end{frame}

% INTRO
\section{Warmup questions}

\begin{frame}[fragile]{\textbf{Q. What is Machine Learning?}}
  \begin{wideitemize}
    \item Machine Learning is fitting a function to examples and using
    that function to generalize and make predictions about
    new examples.
    \item Machine Learning, by large, falls into two categories:\vspace{.4em}
    \begin{wideitemize}
      \item[-] Supervised learning
      \item[-] Unsupervised learning
    \end{wideitemize}
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. How do you represent data in ML?}}
  \begin{wideitemize}
    \item In general, the given data is expressed in a form of a bunch of vectors
    $\vec{v}_{j} \in {\Bbb R}^{d}$ that belong to some high dimensional vector space.
    \item For instance, in image recognition, the vector of an each image is
    a set of pixels (i.e., a pixelated version of the image).
    \item If you have a notion of distance $\Delta(\vec{v}_{i}, \vec{v}_{j})$,
    then you can compare which vectors are close to each other in this high
    dimensional vector space; e.g., the norm $\norm{\vec{v}_{i} - \vec{v}_{j}}^2$
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. What is Supervised Learning?}}
  \begin{wideitemize}
    \item In \textbf{Supervised Learning} (or \textbf{SL}), you are given a
    bunch of examples and their labels (e.g., A or B) and the goal is to
    classify (or assign), when you are given a new example, to which label we
    assign the new example.
    \item \textcolor{blue}{You could think of these labels the name of the
    \textbf{class or cluster} to which certain portions of the data belong.}
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. Can you give an example of Supervised Learning?}}
  \vspace{.4em}
  \begin{wideitemize}
    \item \textcolor{blue}{\textbf{Support vector machines} or \textbf{SVM}}, which
    goal is to construct the optimal separating \textit{hyperplane} between pieces of data; e.g.,
    \begin{wideitemize}
      \item[-] Say a hyperplane between clusters of data represented by labels A and B.
      \item[-] These clusters sit in some high dimensional space, and the idea is to
      construct a plane that maximizes the margins between the plane and the data.
      \item[-] If a new datum sits closer to one area of the data, say A, then
      we assign this new datum to A.
    \end{wideitemize}
    \item (For historical reasons) This algorithm is called \textbf{support
    vector machines} because the vectors that lie on the margin of the plan are
    called the \textit{support} vectors.
  \end{wideitemize}

  \begin{framed}
  This is a method for constructing a device to discriminate. If we're having
  a supervised learning problem then this method gives me an optimal form of
  discrimination.
  \end{framed}

\end{frame}

\note[itemize]{
\item This algorithm has an exponential speed up when you do it quantum mechanically..
}

\begin{frame}[fragile]{\textbf{Q. What is Unsupervised Learning?}}
  \begin{wideitemize}
    \item In \textbf{Unsupervised Learning} (or \textbf{UL}), you are given a
    bunch of data and you are not told it falls naturally into clusters, but
    you are not told what the clusters are.
    \item \textcolor{blue}{The goal is identify the clusters of data, how many clusters there are,
    and then be able to assign new things to these different clusters.}
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. Can you give an example of Unsupervised Learning?}}
  \begin{wideitemize}
    \item \textcolor{blue}{Principal Component Analysis (or \textbf{PCA})} is a classical UL algorithm.
    \item In \textbf{PCA}, the way this works, we construct a \textit{covariance matrix},
    and my covariance matrix is just the following object: $C = \sum_{j} \vec{v}_j\vec{v}^{\dagger}_{j}$,
    where $\vec{v}^{T}_{j}$ is the transpose of $\vec{v}_{j}$.
    \begin{wideitemize}
      \item[-] In other words, we construct $C$ from the data by taking these vectors $\vec{v}_j$ and
      multiply them by their transpose $\vec{v}^{\dagger}_j$.
      \item E.g., Financial forecasting: the vectors could be, for example, can
      represent the changes in stock prices over a 24 hr period, and the
      covariance matrix $C$ would give the correlations (or covariances in the
      data) between the prices of the different stocks in different times within
      the 24 hrs period.
    \end{wideitemize}
    \item In \textbf{PCA}, you diagonalize $C$ and say $C = \sum_{k} P_k
    \vec{\omega}_{k}\vec{\omega}^{\dagger}_{k}$, $P_k$ is piece of the data with size $k$,
    and $\vec{\omega}_{k}$ are the set of vectors you need to find.
    \item If and only if a small set of $P_k >> 0$, then $C$ is effectively low-rank,
    and the corresponding $\vec{\omega}_{k}$ are the principal components.
  \end{wideitemize}

\end{frame}

\note[itemize]{
\item In this stocks example, for instance, if it turns out that all the
  motions of stocks in the stocks market are highly correlated with each other AND
  there is only a few forms of correlations, then this matrix $C$ will be
  effectively low-rank and will only have a few principle components.
\item You see, this PCA is a way of compressing the data. That is, if there
  is only a few principal components then this means that all my vectors can
  be written as the sum of a few $w$s.
\item In general terms, this PCA process is about finding the underlying
  patterns of the data and also gives you a method for data compression.
\item PCA is all about diagonalizing the covariance matrix.
\item PCA is an exercise in linear algebra on very high dimensional vector spaces.
}


\section{Data driven questions}
\begin{transitionframe}
  \begin{center}
    \Huge Harder questions, please!
  \end{center}
\end{transitionframe}



\begin{frame}[fragile]{\textbf{Q. What is cross-validation?}}
  \begin{wideitemize}
    \item Cross-validation is a technique for assessing how well a model
    performs on new independent data.
    \item The simplest example of cross-validation is when you split your
    data into two groups\footnote{e.g., a \~{}60\%-\~{}40\% split}:
    (1) training data, and (2) testing data.
    \item One uses training data to build the model and testing
    data to test the model.
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. How to define/select metrics?}}
\begin{wideitemize}
  \item {\large \textbf{There isn't a one-size-fits-all metric.}}
  \item The metric(s) chosen to evaluate a ML model depends on various factors:
  \begin{wideitemize}
    \item Is it a regression or classification task? E.g., MSE vs Accuracy. 
    \item What is the business objective? E.g., precision vs recall.
    \item What is the distribution of the target variable?
  \end{wideitemize}
  \item Examples of other metrics: Mean Absolute Error (MAE), Mean Squared Error
    (MSE), R-squared, Confusion Matrix and related metrics (Precision, Recall, Accuracy).
\end{wideitemize}
\end{frame}

\note[itemize]{
\item Regression: Mean Squared Percentage Error (MSPE), Mean Absolute Error (MAE),
Minimum Sum of Absolute Error (MSAE), Mean Squared Error (MSE), R-squared, Adjusted R-squared
\item Classification: Confusion Matrix and related metrics (Precision, Recall, Accuracy),
Receiver Operating Characteristics \& Area under the curve (ROC-AUC), log-loss, F1-score
}


\begin{frame}[fragile]{\textbf{Q. Can you explain what precision and recall are?}}
\begin{wideitemize}
  \item \textbf{Recall} is a measure of completeness or quantity, whereas
   \item \textbf{Precision} is a measure of exactness or quality:\vspace{.4em}
  \begin{itemize}
    \item \parbox[t]{1.5in}{$\underbrace{Recall = \frac{TP}{TP +
            FN}}_{\substack{\text{What proportion of actual positives}\\ \text{was identified correctly?}}}$} \hspace{.6in}
      \parbox[t]{1.5in}{$\underbrace{Precision = \frac{TP}{TP + FP}}_{\substack{\text{What
            proportion of positive identifications}\\\text{was actually correct?}}}$}
  \end{itemize}
  \item In simple terms, \textbf{high} precision means your algorithm has returned
  substantially \textit{more relevant results than irrelevant ones}, while
  \textbf{high} recall means your algorithm has returned \textit{most of the
  relevant results}.
\end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. What is a confusion matrix?}}
  \begin{wideitemize}
  \item A \textbf{Confusion Matrix} is a simple way of understanding how well an
    algorithm is doing at classifying data. It is just the idea of \textbf{false
      positives} and \textbf{false negatives}
  \item
    \begin{tabular}{cc|cc}
      \multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{2}{c}{Predicted} \\
      \multicolumn{1}{c}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{No} \\ \hline
      \multirow[c]{2}{*}{\rotatebox[origin=tr]{90}{Actual}} & Yes & TP & FN \\[1.5ex] & No & FP & TN \\ \hline
    \end{tabular}
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. Can you explain what are false positives and
      false negatives?}}
  \begin{wideitemize}
  \item There are two errors that often rear their head when you are learning
    about hypothesis testing —- false positives and false negatives, technically
    referred to as type I error and type II error respectively.
  \item \textbf{False positives} are incorrect classifications of the presence
    of a condition when it is actually absent. A \textbf{false positive} is \textcolor{red}{when you
      reject a true null hypothesis}.
  \item \textbf{False negatives} are incorrect classifications of the absence of
    a condition when it is actually present. A \textbf{false negative} is \textcolor{red}{when you accept
      a false null hypothesis}.
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. Provide examples when false positives are more
      important than false negatives, false negatives are more important than
      false positives and when these two types of errors are equally important}}
  \begin{wideitemize}
  \item E.g., cancer screening. It is much worse to say that someone
    doesn't have cancer when they do (false negative) rather than saying that
    someone has it when in fact they don't (false positive).
  \item E.g., (from a psychological perspective) pregnancy test. Given the null
    hypothesis: ``I am not pregnant.'' A false negative for someone who really
    does not want a child, is not ready for one and when assuring themselves
    with a negative result.
  \item E.g., forecasting (health weather). During the covid-19 outbreak.
    Tracking rate of false positives and false negatives in March 2020 in the
    United States of America. 
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. Can you list some of metrics derived from Confusion Matrix?}}
  \begin{wideitemize}
  \item Confusion matrix related metrics
    \begin{wideitemize}
    \item Accuracy rate: {\footnotesize $\frac{TP + TN}{Total}$}
      where {\footnotesize Total is $TP + TN + FP + FN$},\vspace{-.5em}
    \item Error rate: {\footnotesize $1 - \frac{TP + TN}{Total}$},\vspace{-.5em}
    \item False positive rate: {\footnotesize $\frac{FP}{TN + FP}$},\vspace{-.5em}
    \item Recall: {\footnotesize $\frac{TP}{TP + TN}$}, Precision: {\footnotesize $\frac{TP}{TP + FP}$},\vspace{-.5em}
    \item Specificity: {\footnotesize $1 - \frac{FP}{TN + FP}$},\vspace{-.5em}
    \item Prevalence: {\footnotesize $\frac{TP + FN}{Total}$}
    \end{wideitemize}
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. How do you measure how  good your
      classification algorithm is? You have unbalanced numbers, with our class
      being much larger or smaller than others}}
  \begin{wideitemize}
  \item You use the Matthews correlation coefficient. The number it yields is
    between plus or minus one. Plus one means perfect prediction, zero means no
    better than random.
  \item $\frac{TP x TN - FP x FN}{\sqrt{(TP + FP)(TP + FN)(TN + FP)(TN + FN)}}$
  \end{wideitemize}
\end{frame}


\begin{frame}[fragile]{\textbf{Q. What is linear regression?}}
  \begin{wideitemize}
  \item Linear regression attempts to model the relationship between two continuous
    variables -- a scalar response (or dependent variable) and and one or more
    explanatory variables (or independent variables) -- by fitting a linear
    equation to observed data.
  \item The governing equation for linear regression is also quite simple. It
    takes the form: $y = Bx + A$ where $y$ is the dependent variable, $x$ is the
    independent variable, and $A$ and $B$ are coefficients dictating the equation
  \item e.g. a model that assumes a linear relationship between the input
    variables $x$ and the single output variable $y$.
  \end{wideitemize}
\end{frame}

\begin{frame}[fragile]{\textbf{Q. What is the general form of multiple regression?}}
  \begin{wideitemize}
    \item The general form of the equation for linear regression.
  \end{wideitemize}
\end{frame}

\end{document}
